### 2015-05-08 swmpr_manu.Rnw
removed unused pdfs in figure folder, figures not shown in text

%knitr options
<<setup, cache = F, echo = F>>=
library(knitr)
# set global chunk options
opts_chunk$set(fig.align = 'center', message = F, dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!ht', warning = F, background = 'white', highlight = FALSE, prompt = TRUE, size = 'small')
options(replace.assign=TRUE,width=70,digits=1)
@

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?all\\_params} for individual functions or \\texttt{help.search(`retrieve', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:retrieve', 
  table.env = FALSE
  )
@

@@

<<eval = F, cache = T>>=
# import sample data from package
data(apadbwq)
dat <- apadbwq

@@

# view all attributes of dat
atts <- paste0('\\texttt{', names(attributes(dat)), '}')
atts <- gsub('_', '\\_', atts, fixed = T)
atts_class <- c('character', 'integer', 'character', 'character', 'character', 'logical', 'POSIXct', 'character', 'character')
atts_desc <- c(
  'Column names of the entire data set, inherited from the \\texttt{data.frame} object class',
  'Row names of the data set, inherited from the \\texttt{data.frame} object class',
  'Class of the data object indicating \\texttt{swmpr} and \\texttt{data.frame}',
  'Station identifier used by \\ac{NERRS} as a string with 7 or 8 characters',
  "Character vector of column names for data parameters, e.g., \\texttt{`do\\_mgl'}",
  'Indicates if \\ac{QAQC} columns are present in the raw data',
  'Start and end dates for the raw data',
  'Timezone of the station using the city/country format\\textsuperscript{\\textit{a}}',
  'Class of the \\texttt{datetimestamp} column, usually POSIXct unless data have been aggregated'
)

to_tab <- data.frame(Attributes = atts, Class = atts_class, Description = atts_desc, stringsAsFactors = F)
foot <- c('\\textsuperscript{\\textit{a}}\\footnotesize Time zones that do not observe daylight savings are used for \\texttt{swmpr} objects and may not be cities in the United States.  For example, ``America/Jamaica" is used for Eastern Standard Time.')

@@

latex(
  to_tab[, -1, drop = F],
  file = '',
  caption = "Attributes of a \\texttt{swmpr} object that describe characteristics of the data.",
  rowlabel = 'Attributes',
  colheads = c('Class', 'Description'),
  rowname = to_tab$Attributes,
  caption.loc = 'top',
  insert.bottom = foot,
  col.just=c("p{0.75in}", "p{3.25in}"), 
  label = 'tab:attributes', 
  table.env = FALSE
  )
@

@@

<<eval = F, cache = T>>=
# view available methods for swmpr class
methods(class = 'swmpr')
@

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?comb} for individual functions or \\texttt{help.search(`organize', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:organize', 
  table.env = FALSE
  )
@

<<eval = F, cache = T>>=
# qaqc screen for a swmpr object, retain only '0'
qaqc(dat)

@@

<<eval = F, cache = T>>=
# view the number of observations in each QAQC flag
qaqcchk(dat)
@

@@

<<eval = F, cache = T>>=
# get nutrient data
data(apacpnut)
dat <- apacpnut
dat <- qaqc(dat)

@@

<<eval = F, cache = T>>=
# import data
data(apaebmet)
dat <- apaebmet

@@

<<eval = F, cache = T>>=
# import, qaqc removal
data(apadbwq)
dat <- qaqc(apadbwq)

@@

<<eval = F, cache = T>>=
# get nut, wq, and met data as separate objects
data(apacpnut)
data(apacpwq)
data(apaebmet)
swmp1 <- apacpnut
swmp2 <- apacpwq
swmp3 <- apaebmet

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \\texttt{?aggreswmp} for individual functions or \\texttt{help.search(`analyze', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:analyze', 
  table.env = FALSE
  )
@

<<eval = T, cache = T>>=
# get data, keep all observations
data(apacpnut)
dat <- qaqc(apacpnut, qaqc_keep = NULL)

@@

<<metab_ex, eval = TRUE, cache = TRUE, fig.height = 4, fig.width = 8, warning = FALSE, fig.cap = "Monthly means (95\\% confidence) of ecosystem metabolism estimates (net ecosystem metabolism, gross production, and total respiration) for combined water quality and weather data for two years at Apalachicola Bay, Florida.">>=
## import water quality and weather data
data(apadbwq)
data(apaebmet)

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Miscellaneous functions available from the SWMPr package.  Most are used within the main functions above but may be useful for customized evaluations of \\ac{SWMP} data.  Full documentation for each function is in the help file (e.g., execute \\texttt{?calckl} at the command line).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:misc', 
  table.env = FALSE
  )

@@

% metabolism figure
<<metab_plo, eval = T, cache = T, echo = F, fig.cap = 'Aggregated estimates of net metabolism, gross production, and total respiration for two sites at each \\ac{NERRS} reserve.  Values are daily integrated estimates as mean annual values averaged across all years with 95\\% confidence intervals.  Two sites were chosen from each reserve that had the longest available time series. Sites were assigned to regions based on approximate geographic coordinates.', fig.height = 6, fig.width = 8, out.width = '\\textwidth'>>=
# # packages to use
# library(SWMPr)
# library(httr)
# library(XML)
# library(foreach)
# library(doParallel)
# 
# # names of files on server
# files_s3 <- httr::GET('https://s3.amazonaws.com/swmpalldata/')$content
# files_s3 <- rawToChar(files_s3)
# files_s3 <- htmlTreeParse(files_s3, useInternalNodes = T)
# files_s3 <- xpathSApply(files_s3, '//contents//key', xmlValue)
# files_s3 <- gsub('\\.RData$', '', files_s3) 
# 
# # find only active water quality and weather sites
# # IP address must be registed with CDMO 
# meta <- site_codes()
# sel <- meta$status %in% 'Active' & !grepl('nut$', meta$station_code)
# meta <- meta[sel, ]
# 
# # get wq sites from meta, then filter by those on server
# wq_sites <- grep('wq$', meta$station_code, value = T)
# wq_sites <- files_s3[gsub('\\.RData$', '', files_s3) %in% wq_sites]
# 
# # setup parallel backend for processing
# cl <- makeCluster(8)
# registerDoParallel(cl)
# strt <- Sys.time()
# 
# # process
# metabs <- foreach(wq_site = wq_sites) %dopar% {
#  
#   library(SWMPr)
#   
#   # progress
#   sink('log.txt')
#   cat(wq_site, which(wq_site == wq_sites), 'of', length(wq_sites), '\n')
#   print(Sys.time() - strt)
#   sink()
#   
#   # find corresponding wx station
#   met_site <- substr(wq_site, 1, 3)
#   met_site <- grep(paste0('^', met_site, '.*met'), files_s3, value = T)
#   met_site <- gsub('\\.RData$', '', met_site)
# 
#   # continue if wx data found
#   if(length(met_site) > 0){
#     
#     # if > 1 wx site, pick the one with more obs
#     if(length(met_site) > 1){
# 
#       met_list <- vector('list', length(met_site))
#       names(met_list) <- met_site
#       for(met in met_site){
#       
#         met_tmp <- import_remote(met)
#         met_list[[met]] <- met_tmp
#       
#       }
#     
#       # pick the one with most obs
#       met_most <- which.max(unlist(lapply(met_list, nrow)))
#       met <- met_list[met_most][[1]]
# 
#     # otherwise load only one
#     } else {
#     
#       # met
#       met <- import_remote(met_site)
#     
#     }
#     
#     ##
#     # load the wq file
#     
#     # wq
#     wq <- import_remote(wq_site)
#     
#     ## 
#     # combine, estimate metabolism, reduce data volume
#     dat <- comb(wq, met, method = attr(met, 'station'))
#     dat <- ecometab(dat)
#     dat <- dat[1, ]
#     
#     dat
#     
#   }
#   
# }
# names(metabs) <- wq_sites
# save(metabs, file = 'metabs.RData')

@@

library(Hmisc)
latex(
  metabs_tab[, !names(metabs_tab) %in% c('site', 'region')], 
  file = '', 
  caption = cap, 
  cgroup = c('NEM\\textsuperscript{{\\it a}}', 'Pg', 'Rt'), 
  n.cgroup = c(2, 2, 2), 
  colheads = rep(c('1995-2004', '2005-2014'), 3),
  rowlabel = 'Site', 
  rowname = metabs_tab$site,
  digits = 2,
  insert.bottom = foots,
  rgroup = unique(metabs_tab$region),
  n.rgroup = nrgroups,
  label = 'tab:metab_tab',
  size = 'footnotesize'
  )

@@

\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{figure/swmp_comp.pdf}
\caption{Online application for comparing trends in \ac{SWMP} data parameters using an interactive map.  Link: \href{https://beckmw.shinyapps.io/swmp_comp}{https://beckmw.shinyapps.io/swmp\_comp}}
\label{fig:swmp_comp}
\end{center}
\end{figure}

>>>>

%knitr options
<<setup, cache = F, echo = F>>=
library(knitr)
# set global chunk options
opts_chunk$set(fig.align = 'center', message = F, dev = 'pdf', dev.args = list(family = 'serif'), fig.pos = '!h', warning = F, background = 'white', highlight = FALSE, prompt = TRUE, size = 'small', out.width = '0.00\\textwidth')
options(replace.assign=TRUE,width=70,digits=1)
@

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?all\\_params} for individual functions or \\texttt{help.search(`retrieve', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:retrieve', 
  table.env = FALSE, 
  where = '!tbp'
  )
@

@@

<<eval = F, cache = F>>=
# import sample data from package
data(apadbwq)
dat <- apadbwq

@@

# view all attributes of dat
atts <- paste0('\\texttt{', names(attributes(dat)), '}')
atts <- gsub('_', '\\_', atts, fixed = T)
atts_class <- c('character', 'integer', 'character', 'character', 'character', 'logical', 'POSIXct', 'character', 'character')
atts_desc <- c(
  'Column names of the entire data set, inherited from the \\texttt{data.frame} object class',
  'Row names of the data set, inherited from the \\texttt{data.frame} object class',
  'Class of the data object indicating \\texttt{swmpr} and \\texttt{data.frame}',
  'Station identifier used by \\ac{NERRS} as a string with 7 or 8 characters',
  "Character vector of column names for data parameters, e.g., \\texttt{`do\\_mgl'}",
  'Indicates if \\ac{QAQC} columns are present in the raw data',
  'Start and end dates for the raw data',
'Timezone of the station using the city/country format\\textsuperscript{a}',
  'Class of the \\texttt{datetimestamp} column, usually POSIXct unless data have been aggregated'
)

to_tab <- data.frame(Attributes = atts, Class = atts_class, Description = atts_desc, stringsAsFactors = F)
foot <- c('\\textsuperscript{a}\\footnotesize Time zones that do not observe daylight savings are used for \\texttt{swmpr} objects and may not be cities in the United States.  For example, ``America/Jamaica" is used for Eastern Standard Time.')

@@

latex(
  to_tab[, -1, drop = F],
  file = '',
  caption = "Attributes of a \\texttt{swmpr} object that describe characteristics of the data.",
  rowlabel = 'Attributes',
  colheads = c('Class', 'Description'),
  rowname = to_tab$Attributes,
  caption.loc = 'top',
  insert.bottom = foot,
  col.just=c("p{0.75in}", "p{3.25in}"), 
  label = 'tab:attributes', 
  table.env = FALSE, 
  where = '!tbp'
  )
@

@@

<<eval = F, cache = F>>=
# view available methods for swmpr class
methods(class = 'swmpr')
@

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?comb} for individual functions or \\texttt{help.search(`organize', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:organize', 
  table.env = FALSE, 
  where = '!tbp'
  )
@

<<eval = F, cache = F>>=
# qaqc screen for a swmpr object, retain only '0'
qaqc(dat)

@@

<<eval = F, cache = F>>=
# view the number of observations in each QAQC flag
qaqcchk(dat)
@

@@

<<eval = F, cache = F>>=
# get nutrient data
data(apacpnut)
dat <- apacpnut
dat <- qaqc(dat)

@@

<<eval = F, cache = F>>=
# import data
data(apaebmet)
dat <- apaebmet

@@

<<eval = F, cache = F>>=
# import, qaqc removal
data(apadbwq)
dat <- qaqc(apadbwq)

@@

<<eval = F, cache = F>>=
# get nut, wq, and met data as separate objects
data(apacpnut)
data(apacpwq)
data(apaebmet)
swmp1 <- apacpnut
swmp2 <- apacpwq
swmp3 <- apaebmet

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \\texttt{?aggreswmp} for individual functions or \\texttt{help.search(`analyze', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:analyze', 
  table.env = FALSE, 
  where = '!tbp'
  )
@

<<eval = T, cache = F>>=
# get data, keep all observations
data(apacpnut)
dat <- qaqc(apacpnut, qaqc_keep = NULL)

@@

<<metab_ex, eval = TRUE, cache = T, fig.height = 4, fig.width = 8, warning = FALSE, fig.cap = "Monthly means (95\\% confidence) of ecosystem metabolism estimates (net ecosystem metabolism, gross production, and total respiration) for combined water quality and weather data for two years at Apalachicola Bay, Florida.">>=
## import water quality and weather data
data(apadbwq)
data(apaebmet)

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Miscellaneous functions available from the SWMPr package.  Most are used within the main functions above but may be useful for customized evaluations of \\ac{SWMP} data.  Full documentation for each function is in the help file (e.g., execute \\texttt{?calckl} at the command line).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:misc', 
  table.env = FALSE, 
  where = '!tbp'
  )

@@

% metabolism figure
<<metab_plo, eval = T, cache = T, echo = F, fig.cap = 'Aggregated estimates of net metabolism, gross production, and total respiration for two sites at each \\ac{NERRS} reserve.  Values are daily integrated estimates as mean annual values averaged across all years with 95\\% confidence intervals.  Two sites were chosen from each reserve that had the longest available time series. Sites were assigned to regions based on approximate geographic coordinates.', fig.height = 6, fig.width = 8>>=
# # packages to use
# library(SWMPr)
# library(httr)
# library(XML)
# library(foreach)
# library(doParallel)
# 
# # names of files on server
# files_s3 <- httr::GET('https://s3.amazonaws.com/swmpalldata/')$content
# files_s3 <- rawToChar(files_s3)
# files_s3 <- htmlTreeParse(files_s3, useInternalNodes = T)
# files_s3 <- xpathSApply(files_s3, '//contents//key', xmlValue)
# files_s3 <- gsub('\\.RData$', '', files_s3) 
# 
# # find only active water quality and weather sites
# # IP address must be registed with CDMO 
# meta <- site_codes()
# sel <- meta$status %in% 'Active' & !grepl('nut$', meta$station_code)
# meta <- meta[sel, ]
# 
# # get wq sites from meta, then filter by those on server
# wq_sites <- grep('wq$', meta$station_code, value = T)
# wq_sites <- files_s3[gsub('\\.RData$', '', files_s3) %in% wq_sites]
# 
# # setup parallel backend for processing
# cl <- makeCluster(8)
# registerDoParallel(cl)
# strt <- Sys.time()
# 
# # process
# metabs <- foreach(wq_site = wq_sites) %dopar% {
#  
#   library(SWMPr)
#   
#   # progress
#   sink('log.txt')
#   cat(wq_site, which(wq_site == wq_sites), 'of', length(wq_sites), '\n')
#   print(Sys.time() - strt)
#   sink()
#   
#   # find corresponding wx station
#   met_site <- substr(wq_site, 1, 3)
#   met_site <- grep(paste0('^', met_site, '.*met'), files_s3, value = T)
#   met_site <- gsub('\\.RData$', '', met_site)
# 
#   # continue if wx data found
#   if(length(met_site) > 0){
#     
#     # if > 1 wx site, pick the one with more obs
#     if(length(met_site) > 1){
# 
#       met_list <- vector('list', length(met_site))
#       names(met_list) <- met_site
#       for(met in met_site){
#       
#         met_tmp <- import_remote(met)
#         met_list[[met]] <- met_tmp
#       
#       }
#     
#       # pick the one with most obs
#       met_most <- which.max(unlist(lapply(met_list, nrow)))
#       met <- met_list[met_most][[1]]
# 
#     # otherwise load only one
#     } else {
#     
#       # met
#       met <- import_remote(met_site)
#     
#     }
#     
#     ##
#     # load the wq file
#     
#     # wq
#     wq <- import_remote(wq_site)
#     
#     ## 
#     # combine, estimate metabolism, reduce data volume
#     dat <- comb(wq, met, method = attr(met, 'station'))
#     dat <- ecometab(dat)
#     dat <- dat[1, ]
#     
#     dat
#     
#   }
#   
# }
# names(metabs) <- wq_sites
# save(metabs, file = 'metabs.RData')

@@

library(Hmisc)
latex(
  metabs_tab[, !names(metabs_tab) %in% c('site', 'region')], 
  file = '', 
  caption = cap, 
  cgroup = c('NEM\\textsuperscript{{\\it a}}', 'Pg', 'Rt'), 
  n.cgroup = c(2, 2, 2), 
  colheads = rep(c('1995-2004', '2005-2014'), 3),
  rowlabel = 'Site', 
  rowname = metabs_tab$site,
  digits = 2,
  insert.bottom = foots,
  rgroup = unique(metabs_tab$region),
  n.rgroup = nrgroups,
  label = 'tab:metab_tab',
  size = 'footnotesize', 
  where = '!tbp'
  )

@@

\begin{figure}
\begin{center}
\includegraphics[width = 0\textwidth]{figure/swmp_comp.pdf}
\caption{Online application for comparing trends in \ac{SWMP} data parameters using an interactive map.  Link: \href{https://beckmw.shinyapps.io/swmp_comp}{https://beckmw.shinyapps.io/swmp\_comp}}
\label{fig:swmp_comp}
\end{center}
\end{figure}
